An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
lala

\para{A strawman solution.}
We first present a strawman solution (employed by
previous work~\cite{santolucitoCAV}) that uses 
a set of correct configuration files as a learning set, 
from which it is possible to derive rules 
that must hold with absolute certainty. 
In practice, however, it is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.

@@

In general, each rule can be viewed as a mapping from 
entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
configuration file to a probability function, $P_{rel}$. This can be represented by a rule
$r := (k_1, \ldots, k_n) \rightarrow P_{rel}$.
$P_{rel}$ is a probability function specific to the relation to assess.
The problem with the strawman solution is that the probability functions are restricted to be 
boolean, which is to say that the relation can either be unsatisfied or satisfied, either 0 or 1. 
For instance, for the rule that {\tt max\_connections} must 
be greater than {\tt mysql.max\_persistent}, the rule is denoted by
({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
$B_{>}$ is set to 1. In our approach, we permit the probability functions to take on any value from 0 to 1.

>>>>

\para{A strawman solution.}
We first present a strawman solution (employed by
previous work~\cite{santolucitoCAV}) that uses 
a set of correct configuration files as a learning set, 
from which it is possible to derive rules 
that must hold with absolute certainty. 
In practice, however, it is difficult to obtain a set of files 
that is both guaranteed to be without errors
and large enough to learn sufficiently many rules.
This usually requires manual verification of the learning set, 
which is prone to error.

@@

In general, each rule can be viewed as a mapping from a tuple of 
entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
configuration file to a probability function, $P_{rel}$. This can be represented by a rule
$r := (k_1, \ldots, k_n) \rightarrow P_{rel}$.
$P_{rel}$ is a probability function specific to the relation to assess.
The problem with the strawman solution is that the probability functions are restricted to be 
boolean, which is to say that the relation can either be unsatisfied or satisfied, either 0 or 1. 
For instance, for the rule that {\tt max\_connections} must 
be greater than {\tt mysql.max\_persistent}, the rule is denoted by
({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
$B_{>}$ is set to 1. In our approach, we permit the probability functions to take on any value from 0 to 1.

### 2016-05-10 OSDI/trans.tex
config: fix
lala

\begin{table}
  \begin{tabular}{| l |  l |}
    \hline
    Type &  Template \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\

    \hline
  \end{tabular}
\caption{Table of types, along with associated templates, used in \app}
\label{table:kysymys}
\end{table}

@@

For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
type list by $typelist(e)$.

>>>>

\begin{table}
\caption{Table of types, along with associated templates, used in \app}
  \begin{tabular}{| l |  l |}
    \hline
    Type &  Template \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\

    \hline
  \end{tabular}
\label{table:kysymys}
\end{table}

@@

For an entry $e$, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
type list by $typelist(e)$.
